\section{Lecture 9}

We restate our goal and continue with the Broad estimate.
\begin{theorem}[Decoupling, Bourgain]
    Suppose $f$ is such that $\widehat{f}\subset\Sigma$, where $\Sigma$ is the $N_{1/R}$-nbhd of the truncated paraboloid, 
\end{theorem}
Let's recall the multilinear decoupling theorem. Let $\Sigma=\bigsqcup_j\Sigma_j$, such that for each $j$, we have the normal of $\Sigma_j$ to be close to the $x_j$ axis. And we then separate each $\Sigma_j$ into $\theta$ which are our $R^{-1/2}$ caps. And multilinear decoupling is as follows:
\begin{theorem}[Multilinear Decoupling]
    Let $f_{j,\theta}$ be such that $\widehat{f}_{j,\theta}\subset\theta\subset\Sigma_j$, and we have
    \begin{equation*}
        \|\prod_{j=1}^n|f_j|^{1/n}\|_{L^p}\lesssim R^\epsilon\prod_{j=1}^n\left(\sum_{\theta}\|f_{j,\theta}\|_{L^p}^2 \right)^{\frac{1}{2}\frac{1}{n}}
    \end{equation*}
\end{theorem}

We state the main lemma which contains the broad and narrow estimate as two terms.
\begin{lemma}[Main]
    For $2\leq p\leq\frac{2n}{n-1}$, we have
    \begin{equation*}
        D_{p,n}(R)\lesssim K^{O(1)}MD_{p,n}(R)+D_{p,n-1}(K^2)D_{p,n}(R/K^2)
    \end{equation*}
\end{lemma}
Hence by indunction on both scale $R$ and dimension $n$, note the allowable range for $p$ increases as $n$ decreases, hence by induction, we are able to conclude the main theorem.

For the broad estimate, we would like to show
\begin{equation*}
    \|f\|_{L^p(Broad)}\lesssim K^{O(1)}R^\epsilon\left(\sum\|f_\theta\|_{L^p}^2 \right)^{1/2}
\end{equation*}
And for the narrow estimate, we've shown that for $\tau$, which are $K^{-1}$ caps that contain $\theta$ caps, we have
\begin{equation*}
    \|f\|_{L^p(Narrow)}\lesssim D_{p,n-1}(K^2)\left(\sum\|f_\tau\|_{L^p}^2 \right)^{1/2}
\end{equation*}
And by decoupling at the scale of $R/K^2$, hence if we rescale $\tau$ to the paraboloid, we would get $K/R^{1/2}$, hence we have
\begin{equation*}
    \|f_\tau\|_{L^p}\lesssim D_{p,n}(R/K^2)\left(\sum_{\theta\subset\tau}\|f_\theta\|_{L^p}^2 \right)^{1/2}
\end{equation*}
We then would have recovered the main lemma.

Now we show the broad estimate.

